|

### 2019-09-03 article/article.Rmd
Small change last paragraph.
Map line width changes.

## Map manipulation test -- Intervention 2
mapbr <- get_brmap('City')
gaaux <- filter(ga, phase2 == 1)
gaaux <- select(gaaux, ibge_code7, downl)
gaaux <- rename(gaaux, City = ibge_code7)
gaaux <- unique(gaaux)
gaaux$City <- as.numeric(gaaux$City)
gaaux2 <- impact_evaluation_phase2 %>%
  select(ibge_code7) %>%
  transmute(City = as.numeric(ibge_code7)) %>%
  unique()
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 0
gaaux2 <- data.frame(City = mapbr$City)
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 2
gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads',
                                                  'Not in App'))
mapbr <- join_data(mapbr, gaaux, by = 'City')
p1 <- ggplot() + 
  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.02) +
  scale_fill_manual(values=c( "#E69F00", "#0072B2", "#F0E442")) +
  theme_map()
p1

@@

In sum, our experiments suggest that popular participation and bottom-up monitoring may not be effective to improve public service delivery in the case of school constructions in Brazil. Nevertheless, the null findings are informative to researchers and policy-makers. The most important recommendation derived from this study is that interventions targeting elite groups, such as lobbyists or civil servants, might render better policy outcomes than those focused at the grassroots levels. Another core lesson is that although digital interventions are promising means to deliver information, perhaps they do not have the same impact as personal, face-to-face communication. Since many developing countries share Brazil's issues with education provision, the shortcomings we describe here serve as warnings for future interventions.

>>>>

## Map manipulation test -- Intervention 2
mapbr <- get_brmap('City')
gaaux <- filter(ga, phase2 == 1)
gaaux <- select(gaaux, ibge_code7, downl)
gaaux <- rename(gaaux, City = ibge_code7)
gaaux <- unique(gaaux)
gaaux$City <- as.numeric(gaaux$City)
gaaux2 <- impact_evaluation_phase2 %>%
  select(ibge_code7) %>%
  transmute(City = as.numeric(ibge_code7)) %>%
  unique()
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 0
gaaux2 <- data.frame(City = mapbr$City)
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 2
gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads',
                                                  'Not in App'))
mapbr <- join_data(mapbr, gaaux, by = 'City')
p1 <- ggplot() + 
  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.01) +
  scale_fill_manual(values=c( "#E69F00", "#0072B2", "#F0E442")) +
  theme_map()
p1

@@

In sum, our experiments suggest that popular participation and bottom-up monitoring may not be effective to improve public service delivery in the case of school constructions in Brazil. Nevertheless, the null findings are informative to researchers and policy-makers. The most important recommendation derived from this study is that interventions targeting elite groups, such as lobbyists or civil servants, might render better policy outcomes than those focused at the grassroots levels. Another core lesson is that although digital interventions are promising means to deliver information, perhaps they do not have the same impact as personal, face-to-face communication. Since many developing countries share Brazil's issues with education provision, the shortcomings we describe here serve as warnings for future interventions. Finally, whether this study generalises beyond school constructions to other bottom-up programs, and to other contexts, remains to be studied.
